High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-04-04 notebooks/synthetic.qmd
more work on synthetic

```{julia}
results = DataFrame()
for (dataname, data) in datasets

@@

```{julia}
function plot_ce(results; dataset=:multi_class, classifier=:mlp, λ=0.1, img_height=300, zoom=-0.2)
    df_plot = results[results.dataset .== dataset,:] |>
        res -> res[res.classifier .== classifier,:] |>
        res -> res[res.λ .== λ,:]
    plts = map(eachrow(df_plot)) do row
        Plots.plot(
            row.ce,
            title="cov: $(row.coverage), temp: $(row.temperature)",
            cbar=false,
            zoom=zoom,
            legend=false,
        )
    end
    nrow = length(cvgs)
    ncol = length(temps)
    _layout = (nrow, ncol)
    Plots.plot(
        plts..., 
        size=img_height.*reverse(_layout), layout=_layout,
        plot_title="λ: $λ, dataset: $dataset, classifier: $classifier",
    )
end
```

```{julia}
plot_ce(results; λ=Λ[1], dataset=:moons)
```

>>>>

```{julia}
#| echo: false

results = DataFrame()
for (dataname, data) in datasets

@@

```{julia}
#| echo: false

function plot_ce(results; dataset=:multi_class, classifier=:mlp, λ=0.1, img_height=300, zoom=-0.2)
    df_plot = results[results.dataset .== dataset,:] |>
        res -> res[res.classifier .== classifier,:] |>
        res -> res[res.λ .== λ,:]
    plts = map(eachrow(df_plot)) do row
        Plots.plot(
            row.ce,
            title="cov: $(row.coverage), temp: $(row.temperature)",
            cbar=false,
            zoom=zoom,
            legend=false,
        )
    end
    nrow = length(cvgs)
    ncol = length(temps)
    _layout = (nrow, ncol)
    Plots.plot(
        plts..., 
        size=img_height.*reverse(_layout), layout=_layout,
        plot_title="λ: $λ, dataset: $dataset, classifier: $classifier",
    )
end
```

```{julia}
#| output: true
#| echo: false

for dataset in keys(datasets)
    Markdown.parse("""### $dataset""")
    for classifier in keys(classifiers)
        Markdown.parse("""#### $classifier""")
        Markdown.parse("""::: {.panel-tabset}""")
        for λ in Λ
            Markdown.parse("""##### λ: $λ""")
            display(plot_ce(results; dataset=dataset, classifier=classifier, λ=λ))
        end
        Markdown.parse(""":::""")
    end
end
```

## Benchmark

```{julia}
generators = Dict(
    :wachter => GenericGenerator(opt=opt, λ=l2_λ),
    :revise => REVISEGenerator(opt=opt, λ=l2_λ),
    :greedy => GreedyGenerator(opt=opt),
)

# Untrained Models:
models = Dict("cov$(cov)" => CCE.ConformalModel(conformal_model(mlp; method=:simple_inductive, coverage=cov)) for cov in cvgs)
```

```{julia}
bmks = []
measures = [
    CounterfactualExplanations.distance,
    CCE.distance_from_energy,
    CCE.distance_from_targets,
    CounterfactualExplanations.validity,
]
for (dataname, dataset) in datasets
    for λ in Λ, temp in temps
        _generators = deepcopy(generators)
        _generators[:cce] = CCEGenerator(temp=temp, λ=[l2_λ,λ], opt=opt)
        _generators[:energy] = CCE.EnergyDrivenGenerator(λ=[l2_λ,λ], opt=opt)
        _generators[:target] = CCE.TargetDrivenGenerator(λ=[l2_λ,λ], opt=opt)
        bmk = benchmark(
            dataset; 
            models=deepcopy(models), 
            generators=_generators, 
            measure=measures,
            suppress_training=false, dataname=dataname,
            n_individuals=5,
            initialization=:identity,
        )
        bmk.evaluation.λ .= λ
        bmk.evaluation.temperature .= temp
        push!(bmks, bmk)
    end
end
bmk = reduce(vcat, bmks)
```

```{julia}
CSV.write(joinpath(output_path, "synthetic_benchmark.csv"), bmk())
```

```{julia}
#| output: true
#| echo: false

df = bmk()
for dataname ∈ sort(unique(df.dataname))
    Markdown.parse("""### $dataset""")
    df_ = df[df.dataname .== dataname, :]
    for λ in Λ, temp in temps
        Markdown.parse("""#### λ: $λ""")
        df_plot = df_[df_.λ .== λ, :]
        df_plot = df_plot[df_plot.temperature .== temp, :]
        plt = AlgebraOfGraphics.data(df_plot) * visual(BoxPlot) * 
            mapping(:generator, :value, row=:variable, col=:model, color=:generator)
        plt = draw(
            plt, axis=(xlabel="", xticksvisible=false, xticklabelsvisible=false, width=200, height=180), 
            facet=(; linkyaxes=:minimal)
        )   
        display(plt)
    end
end
```
